Predicting the Capture Rate of Pokemon

### 2022-12-10 Draft2.Rmd
commit

```{r}
# Creating recipe
pokemon_recipe <- recipe(capture_rate ~ base_total + base_happiness + experience_growth + height_m + percentage_male + weight_kg + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>% 
  # imputing percentage male
  step_impute_linear(percentage_male, impute_with = imp_vars(base_total, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # imputing height
  step_impute_linear(height_m, impute_with = imp_vars(base_total, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # imputing weight
  step_impute_linear(weight_kg, impute_with = imp_vars(base_total, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  step_other(type1) %>% 
  # dummy coding nominal variables
  step_dummy(generation, is_legendary, type1, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate) %>% 
  # normalizing
  step_center(all_predictors()) %>% 
  step_scale(all_predictors())
```

@@

```{r}
# Fitting the models
lm_fit <- fit_resamples(lm_workflow, resamples = pokemon_folds)
```

```{r}
collect_metrics(lm_fit)
```

@@

ridge_workflow <- workflow() %>% 
  add_recipe(ridge_lasso_recipe) %>% 
  add_model(ridge_spec)

@@

tune_res <- tune_grid(
  ridge_workflow,
  resamples = pokemon_folds,
  grid = penalty_grid
)
```
```{r}
autoplot(tune_res)
```

```{r}
best_penalty <- select_best(tune_res, metric = 'rmse')

ridge_final <- finalize_workflow(ridge_workflow, best_penalty)
ridge_final_fit <- fit_resamples(ridge_final, resamples = pokemon_folds)
collect_metrics(ridge_final_fit)
```

@@

tune_res2 <- tune_grid(
  lasso_workflow,
  resamples = pokemon_folds,
  grid = penalty_grid
)
```

```{r}
autoplot(tune_res2)
```

```{r}
best_lasso_penalty <- select_best(tune_res2, metric = "rmse")
lasso_final <- finalize_workflow(lasso_workflow, best_lasso_penalty)
lasso_final_fit <- fit_resamples(lasso_final, resamples = pokemon_folds)
```

@@

```{r, message = FALSE, warning = FALSE}
poly_rec <- pokemon_recipe %>% 
  step_poly(attack, defense, hp, sp_attack, sp_defense, speed, degree = tune())

@@

lm_spec <- linear_reg() %>% 
  set_mode("regression") %>% 
  set_engine("lm")

poly_wf <- workflow() %>% 
  add_model(lm_spec) %>% 
  add_recipe(poly_rec)

@@

tune_res3 <- tune_grid(
  poly_wf,
  resamples = pokemon_folds,
  grid = degree_grid
)
autoplot(tune_res3)
```

```{r}
best_poly<- select_best(tune_res3, metric = "rmse")
poly_final <- finalize_workflow(poly_wf, best_poly)
poly_final_fit <- fit_resamples(poly_final, resamples = pokemon_folds)

@@

### KNN  
```{r}
knn_model <- nearest_neighbor(
  neighbors = tune(),
  mode = "regression") %>% 
  set_engine("kknn")

@@

knn_parameters <- parameters(knn_model)

knn_grd <- grid_regular(knn_parameters, levels = 5)

knn_tune <- tune_grid(
    knn_workflow,
    resamples = pokemon_folds,
    grid = knn_grd
  )
```

@@

```{r}
best_knn <- select_best(knn_tune, metric = "rmse")
knn_final <- finalize_workflow(knn_workflow, best_knn)
knn_final_fit <- fit_resamples(knn_final, resamples = pokemon_folds)
```

@@

elastic_tune <- tune_grid(
  elastic_workflow,
  resamples = pokemon_folds,
  grid = elastic_grid
)
```

```{r}
autoplot(elastic_tune)
```

@@

@@

# Creating a regular grid with 8 levels each
rf_parameter_grid <- grid_regular(mtry(range = c(1, 19)), trees(range = c(200,1000)), min_n(range = c(5,20)), levels = 8)
```

@@

```{r}
# Finding roc_auc of best performing random forest model on folds
rf_best_roc_auc <- rf_tuned %>% 
  collect_metrics() %>% 
  arrange(mean)

rf_best_roc_auc
```

```{r}
best_rf <- select_best(rf_tuned)
rf_final_workflow <- finalize_workflow(rf_workflow, best_rf)
rf_final_fit <- fit(rf_final_workflow, data = pokemon_train)

rf_final_fit %>% 
  extract_fit_engine() %>% 
  vip()
```

### BOOSTED TREE
```{r}
# Setting up boosted tree model
boosted_spec <- boost_tree(trees = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

@@

# Creating regular grid
boosted_grid <- grid_regular(trees(range = c(10, 2000)), levels = 10)
```

@@

# Printing autoplot of results
autoplot(boosted_tuned)
```

```{r}
# Finding roc_auc of best performing boosted tree model on folds
boosted_best_roc_auc <- boosted_tuned %>% 
  collect_metrics() %>% 
  arrange((mean))

boosted_best_roc_auc
```

>>>>

```{r}
# Creating recipe
pokemon_recipe <- recipe(capture_rate ~ base_total + base_happiness + experience_growth + height_m + percentage_male + weight_kg + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>% 
  # imputing percentage male
  step_impute_linear(percentage_male, impute_with = imp_vars(base_total, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # imputing height
  step_impute_linear(height_m, impute_with = imp_vars(base_total, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # imputing weight
  step_impute_linear(weight_kg, impute_with = imp_vars(base_total, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # Only prioritizing top types of Pokemon
  step_other(type1) %>% 
  # dummy coding nominal variables
  step_dummy(generation, is_legendary, type1, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate) %>% 
  # normalizing
  step_center(all_predictors()) %>% 
  step_scale(all_predictors())
```

@@

```{r}
# Fitting the models
lm_fit <- fit_resamples(lm_workflow, resamples = pokemon_folds)

# Save
write_rds(lm_fit, file = "lm_final.rds")
```

```{r}
lm_final_fit <- read_rds(file = "lm_final.rds")

collect_metrics(lm_final_fit)
```

@@

ridge_workflow <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(ridge_spec)

@@

ridge_tune <- tune_grid(
  ridge_workflow,
  resamples = pokemon_folds,
  grid = penalty_grid
)

write_rds(ridge_tune, file = "ridge.rds")
```
```{r}
ridge_tune <- read_rds(file = "ridge.rds")

autoplot(ridge_tune)
```

```{r}
best_penalty <- select_best(ridge_tune, metric = 'rmse')

ridge_final <- finalize_workflow(ridge_workflow, best_penalty)
ridge_final_fit <- fit_resamples(ridge_final, resamples = pokemon_folds)

write_rds(ridge_final_fit, file = "ridge_final.rds")

ridge_final_fit <- read_rds(file = "ridge_final.rds")

collect_metrics(ridge_final_fit)
```

@@

lasso_tune <- tune_grid(
  lasso_workflow,
  resamples = pokemon_folds,
  grid = penalty_grid
)

write_rds(lasso_tune, file = "lasso.rds")

lasso_tune <- read_rds(file = "lasso.rds")
```

```{r}
autoplot(lasso_tune)
```

```{r}
best_lasso_penalty <- select_best(tune_res2, metric = "rmse")
lasso_final <- finalize_workflow(lasso_workflow, best_lasso_penalty)
lasso_final_fit <- fit_resamples(lasso_final, resamples = pokemon_folds)

write_rds(lasso_final_fit, file = "lasso_final.rds")

lasso_final_fit <- read_rds(file = "lasso_final.rds")

@@

```{r, message = FALSE, warning = FALSE}
poly_rec <- pokemon_recipe %>% 
  step_poly(base_total, base_happiness, experience_growth, height_m, percentage_male, weight_kg, degree = tune())

@@

poly_spec <- linear_reg() %>% 
  set_mode("regression") %>% 
  set_engine("lm")

poly_wf <- workflow() %>% 
  add_model(poly_spec) %>% 
  add_recipe(poly_rec)

@@

poly_tuned <- tune_grid(
  poly_wf,
  resamples = pokemon_folds,
  grid = degree_grid
)

write_rds(poly_tuned, file = "poly.rds")
poly_tuned <- read_rds(file = "poly.rds")

autoplot(poly_tuned)
```

```{r}
best_poly<- select_best(poly_tuned, metric = "rmse")
poly_final <- finalize_workflow(poly_wf, best_poly)
poly_final_fit <- fit_resamples(poly_final, resamples = pokemon_folds)

write_rds(poly_final_fit, file = "poly_final.rds")

poly_final_fit <- read_rds(file = "poly_final.rds")

@@

### KNN  
```{r, warning=FALSE}
knn_model <- nearest_neighbor(
  neighbors = tune(),
  mode = "regression") %>% 
  set_engine("kknn")

@@

knn_grid <- grid_regular(neighbors(range = c(1,15)), levels = 5)

knn_tune <- tune_grid(
    knn_workflow,
    resamples = pokemon_folds,
    grid = knn_grid
  )

write_rds(knn_tune, file = "knn.rds")

knn_tune <- read_rds(file = "knn.rds")

@@

```{r}
best_knn <- select_best(knn_tune, metric = "rmse")
knn_final <- finalize_workflow(knn_workflow, best_knn)
knn_final_fit <- fit_resamples(knn_final, resamples = pokemon_folds)

write_rds(knn_final_fit, file = "knn_final.rds")

knn_final_fit <- read_rds(file = "knn_final.rds")
```

@@

elastic_tune <- tune_grid(
  elastic_workflow,
  resamples = pokemon_folds,
  grid = elastic_grid
)

write_rds(elastic_tune, file = "elastic.rds")
```

```{r}
elastic_tune <- read_rds(file = "elastic.rds")

autoplot(elastic_tune)
```

```{r}
# Finding roc_auc of best performing random forest model on folds
elastic_best_rmse <- elastic_tune %>% 
  collect_metrics() %>% 
  arrange(mean)  %>% 
  slice(73)

elastic_best_rmse
```

@@

write_rds(elastic_final_fit, file = "elastic_final.rds")

elastic_final_fit <- read_rds(file = "elastic_final.rds")

@@

# Creating a regular grid with 8 levels each
rf_parameter_grid <- grid_regular(mtry(range = c(1, 14)), trees(range = c(200,1000)), min_n(range = c(5,20)), levels = 8)
```

@@

```{r}
# Finding roc_auc of best performing random forest model on folds
rf_best_rmse <- rf_tuned %>% 
  collect_metrics() %>% 
  arrange(mean) %>% 
  slice(513)

rf_best_rmse
```

```{r}
best_rf <- select_best(rf_tuned)
rf_final_workflow <- finalize_workflow(rf_workflow, best_rf)
rf_final_fit <- fit_resamples(rf_final_workflow, resamples = pokemon_folds)

write_rds(rf_final_fit, file = "rf_final.rds")

rf_final_fit <- read_rds(file = "rf_final.rds")

collect_metrics(rf_final_fit) %>% slice(1)
```

```{r}
best_rf2 <- select_best(rf_tuned)
rf_final_workflow2 <- finalize_workflow(rf_workflow, best_rf)
rf_final_fit2 <- fit(rf_final_workflow, data = pokemon_train)

rf_final_fit2 %>% 
  extract_fit_engine() %>% 
  vip()
```

### BOOSTED TREE
```{r}
# Setting up boosted tree model
boosted_spec <- boost_tree(trees = tune(),
                          learn_rate = tune(),
                          min_n = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

@@

# Creating regular grid
boosted_grid <- grid_regular(trees(range = c(5, 200)), learn_rate(range = c(0.01,0.1), trans = identity_trans()), min_n(range = c(40, 60)), levels = 5)
```

@@

# Printing autoplot of results
autoplot(boosted_tuned, metric = 'rmse')
```

```{r}
# Finding roc_auc of best performing boosted tree model on folds
boosted_best_rmse <- boosted_tuned %>% 
  collect_metrics() %>% 
  arrange(mean) %>% 
  slice(126)

boosted_best_rmse
```

```{r, eval = FALSE, warning = FALSE}
# Elastic
elastic_tuned <- read_rds(file = "elastic_tune.rds")

# Fitting best random forest model to the folds
best_elastic <- select_best(elastic_tuned)
elastic_final_workflow <- finalize_workflow(elastic_workflow, best_elastic)
elastic_final_fit <- fit_resamples(elastic_final_workflow, resamples = pokemon_folds)

# Save
write_rds(rf_final_fit, file = "elastic_final.rds")

# Polynomial Regression
poly_tuned <- read_rds(file = "poly_tuned.rds")

# Fitting best random forest model to the folds
best_poly <- select_best(poly_tuned)
poly_final_workflow <- finalize_workflow(poly_wf, best_poly)
poly_final_fit <- fit_resamples(poly_final_workflow, resamples = pokemon_folds)

# Save
write_rds(rf_final_fit, file = "poly_final.rds")

# Random Forest
rf_tuned <- read_rds(file = "rf.rds")

# Fitting best random forest model to the folds
best_rf <- select_best(rf_tuned)
rf_final_workflow <- finalize_workflow(rf_workflow, best_rf)
rf_final_fit <- fit_resamples(rf_final_workflow, resamples = pokemon_folds)

# Save
write_rds(rf_final_fit, file = "rf_final.rds")

# Boosting
boosted_tuned <- read_rds(file = "boosted.rds")

# Fitting best boosted trees model to the folds
best_boosted <- select_best(boosted_tuned)
boosted_final_workflow <- finalize_workflow(boosted_workflow, best_boosted)
boosted_final_fit <- fit_resamples(boosted_final_workflow, resamples = pokemon_folds)

# Save
write_rds(boosted_final_fit, file = "boosted_final.rds")
```

```{r}
